Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV

### 2018-01-15 appendix.tex
adding the appendix

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} for two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_A1}
              \end{center}
\end{figure*}

The measured $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}. In these calculations the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
The calculations capture the centrality dependence of $v_n$ in the central and mid-central collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are shown in different colors. The results for different $\eta/s$ values are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber and, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_A2}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to mid-central collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3 and 4). The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$. The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10--20\%.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT}}
        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
        \label{fig:Figure_A3}
              \end{center}
\end{figure*}

The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A3}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_A3} within 20\% for $v_2$ and 10\% for $v_3$ and $v_4$. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
The default version of AMPT underestimates $v_n$ for $n$ = 2--4 by $\approx$ 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

>>>>

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v2_comp_EKRT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v3_comp_EKRT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA1_v4_comp_EKRT}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} for two different $\eta/s(T)$ parametrizations, labeled in the same way as in Ref.~\cite{Niemi:2015qia}.}
        \label{fig:Figure_A1}
              \end{center}
\end{figure*}

The measured $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_A1}. In these calculations, the initial conditions and $\eta/s$ parametrizations are chosen to reproduce the LHC $v_n$ data.
The calculations capture the centrality dependence of $v_n$ in the central and mid-central collisions within 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v2_comp_VISH}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v3_comp_VISH}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA2_v4_comp_VISH}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--4 in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN, and MC-Glauber are shown in different colors. The results for different $\eta/s$ values are shown as different line styles, the small shear viscosity ($\eta/s = 0.08$) are shown as solid lines, and large shear viscosities ($\eta/s = 0.2$ for MC-KLN and MC-Glauber and, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_A2}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$, and $v_4$. In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to mid-central collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3, and 4). The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$. The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10--20\%.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v2_comp_AMPT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v3_comp_AMPT}}\hspace{-0.27cm}
                       \resizebox{0.34\textwidth}{!}{\includegraphics{figs/FigA3_v4_comp_AMPT}}
        \caption{The individual flow harmonics $v_n$ ($n$ = 2, 3, and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf}. Results are compared to various AMPT models.}
        \label{fig:Figure_A3}
              \end{center}
\end{figure*}

The AMPT calculations with various configurations are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A3}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_A3} within 20\% for $v_2$ and 10\% for $v_3$ and $v_4$. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data compared to the calculations with the string melting version of AMPT, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
The default version of AMPT underestimates $v_n$ for $n$ = 2--4 by $\approx$ 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants [NSC($m$,$n$)] quantitively for most centralities while the string melting AMPT model fails to describe them.
